---
title: "Homework 2"
author: "Angela Zhang"
date: "10/9/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Writing your own function

I named my function, myFunction, that takes the options, "data", "na.rm", and "abline". The "if" loop specifies whether or not the abline shows the median or the mean.
```{r}
myFunction = function(data,na.rm=T,abline="mean"){
  mean_data = mean(data, na.rm = na.rm)
  median_data = median(data, na.rm = na.rm)
  stripchart(data,pch =20)
  if (abline == "mean"){
    abline(v = mean_data)
  }
  else{
    abline(v = median_data)
  }
  central = c(mean_data, median_data, as.numeric(sum(is.na(data))))
  names(central) = c("Mean","Median","Number of NAs")
  print(central)
}


set.seed(1234)
my_data <- c(rgamma(50, shape = 5, rate = 1), NA)

myFunction(my_data, na.rm=T)
```

## Looping with functional programming

(a)
```{r}
mean_sd = function(x, ...){
  c(mean(x, ...), sd = sd(x, ...))
}

apply(airquality, 2, function(x){by(x, list(toohot = airquality$Temp > 85), mean_sd)})
```

The results produce the same numbers but looks much messier than subsetting the list first by temperature and then finidng the mean and standard deviation of the columns.

(b) I will use the dataset Beaver1


```lapply``` returns a list of values. It takes a dataset and applies a function to all columns of the dataset. For example, I took the mean of all the variables in the beaver1 dataset and I got the means for day, time, temp, and activity. 

```{r}
lapply(beaver1, mean)
```

The ```mapply``` function gives us a way to use non-vectorized functions. For example, if you want to create a matrix with the same rows, instead of

```{r}
matrix(c(rep(1, 3), rep(2, 3), rep(3, 3)),nrow=3,ncol=3)
```

We can use ```mapply``` instead. This takes the "rep" function with the vector 1:3, and replicates it three times

```{r}
mapply(rep,1:3,3)
```
## Bootstrapping

I entered the response as a vector containing the 5 responses. From Lecture 2 notes, I sampled with replacement from the "response" variable 10,000 times to get 10,000 variables. With this vector, I applied the 'var' function to get the variance.

```{r}
response = c(1,5,8,3,7)

many_medians = replicate(10000, median(sample(response, size = 5, replace = T)))
var(many_medians)
```