  ---
title: "Homework 3"
author: "Angela Zhang"
date: "10/12/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting started with Tidyverse

(a) 

```{r} 
apply(faithful,2,mean)
```

(b)
```{r}
library(magrittr)

faithful %>%
  apply(2,mean)
```

(c)

I loaded the package ```tidyverse``` in order to use the pipe operator
```{r}
library(tidyverse)

faithful %>%
  summarize(mean = mean(eruptions))
```

(d)

I used the function ```summarize_all```
```{r}
faithful %>%
  summarize_all(mean)
```

(e)

272 lines are shown by default. If you convert it to a tibble, only 10 lines of the data is shown. Tibble also informs you how many more rows there are in the dataset (that wasn't outputted).
```{r}
dim(faithful)

as.tibble(faithful)
```

## Intuitive data exploration

(a)
Subset is part of base R and doesn't discard row names. Filter is part of dplyr. Subset can be used to select columns while ```dplyr``` uses the function ```select```. Subset is used interactively (convenience function) while filter can be used in programming. We will use the function ```filter```

(b)
```{r}
airquality %>%
  filter(Temp > 85) %>%
  summarize(mean = mean(Ozone, na.rm = T), sd = sd(Ozone, na.rm = T))
```

(c)

The results that we get are the same but the first method (with ```tidyverse```) is more intuitive.
```{r}
airquality %>%
  group_by(Temp > 85) %>%
  summarize(mean = mean(Ozone, na.rm = T), sd = sd(Ozone, na.rm = T))

## using by() (from lecture 2)
by(airquality$Ozone, list(month = airquality$Month), mean, na.rm = TRUE)
```

## Function composition

(a)

```f <- . %>% cos %>% sin``` creates the function ```sin(cos(x))``` where the user provides the ```x```. For example:

```{r}
f <- . %>% cos %>% sin

f(2)
sin(cos(2))
```

(b)

The compound pipe operator ```%<>%``` is used as shorthand notation in cases where you overwrite a variable. For example, I used instead of using ```beaver1$temp <- sqrt(beaver1$temp) ```,you can use the command ```beaver1 %<>% sqrt``` to achieve the same effect of finding the square root of all the temperatures in the ```beaver1``` dataset.

(c)

I wrote a function that converts Fahrenheit to Celsius and then I used that function with the compound pipe operator
```{r}
head(airquality$Temp)

FtoC <- function(x){round((x-32)*(5/9),0)} # This function is not necessarily anymore
                                           # since I inputted it below.

airquality$Temp %<>% (function(x){round((x-32)*(5/9),0)}) 

head(airquality$Temp)
```