---
title: "Homework 8"
author: "Angela Zhang"
date: "11/26/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
library(tidyverse)
library(xtable)

```

## Question 1: Running R scripts from the command line

a) We are interested in estimating $\hat\beta$, i.e the slope of the regression line.

b)

```{r}
library(sandwich)
```

c) The script does not give any standard errors but does provide coverage. The model gives a coverage of 0.5 while the sandwich method gives a coverage of 0.3. 

d) I got the same answers as before but it was outputted in a new file.


## Question 2: Running R scripts on ```cox```

It look 42 seconds to run. The model gives a coverage of 0.748 and the sandwich model has a coverage of 0.9494.


## Question 3: Running R scripts on the clusters

a) Running both scripts resulted in 15 text files and 15 Rdata files.

b)

\begin{table}[ht]
\centering
\begin{tabular}{rlrrr}
  \hline
 & n & x & model & sandwich \\ 
  \hline
  & n20 & 2.003 & 0.7324 & 0.8364 \\ 
  & n400 & 2.0001 & 0.7374 & 0.9474 \\ 
  & n600 & 1.9999 & 0.7458 & 0.9436 \\ 
   \hline
\end{tabular}
\end{table}


## Appendix

###3b

```

n = c("n20","n400","n600")

list = list()
for(i in 1:3){
  filelist = list.files(pattern = paste(n[i],".*.txt",sep =""))
  datalist = lapply(filelist, function(x) unlist(strsplit(readLines(x)[4]," ")) )
  datafr = do.call("rbind", datalist)
  frame = data.frame(n = n[i], x = as.numeric(datafr[,1]), 
                     model = as.numeric(datafr[,2]), 
                     sandwich = as.numeric(datafr[,3] ))
  print(frame)
  list[[i]] = frame
}

full_list = do.call("rbind", list)

full_list %>%
  group_by(n)%>%
  summarize(x = mean(x), model = mean(model), sandwich = mean(sandwich))%>%
  xtable
```